intro

### 2021-10-04 06_Paper/ER-ED/intro.Rmd
added text

Das ist nur eine Test-Intro

>>>>

# 1. Introduction

[...]
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

## Adapting an effort discounting paradigm

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: we have to change the assumption that the easiest *N*-back level has the highest SV.
That is necessary, because there is nothing like an objectively easier and less effortful strategy.
As we have shown in previous studies, there are inter-individual differences in the preference of ER strategies [Scheffel2021].
